Inference for trans-dimensional Bayesian models with Diffusive Nested Sampling

### 2014-06-27 Documents/Paper/ms.tex
New references

>>>>

\bibitem[Bretthorst(1988)]{bretthorst} Bretthorst, G.~Larry.\  1988.\
Bayesian Spectrum Analysis and Parameter Estimation.\ In Lecture Notes in
Statistics, 48, Springer-Verlag, New York, New York.

\bibitem[Brewer et al.(2007)]{2007ApJ...654..551B} Brewer, B.~J., Bedding, 
T.~R., Kjeldsen, H., Stello, D.\ 2007.\ Bayesian Inference from 
Observations of Solar-like Oscillations.\ The Astrophysical Journal 654, 
551-557.
